\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
Solidify our explanation about why we can't do hoverable information on a signal of trees

The obvious type for a menu structure that may change is \texttt{Signal (Tree
String)}. It is easy enough to convert a value of this type to one of type
\texttt{Signal (Tree Element)}, but we cannot add hover detection to this tree.
We are able to map from \texttt{Signal Element -> (Signal Element,
Signal Bool)}, but not (in any useful way) from \texttt{Element ->
(Element, Bool)}. That is, because the tree is already a signal, we cannot
create signals inside it (without creating signals of signals). Hover
information requires a (distinct) signal at each item in the tree.

>>>>

The obvious type for a menu structure that may change is \texttt{Signal (Tree
String)}.  It is easy enough to convert a value of this type to one of type
\texttt{Signal (Tree Element)}, but we cannot add hover detection to this tree.
We are able to map from \texttt{Signal Element -> (Signal Element, Signal
Bool)}, but not (in any useful way) from \texttt{Element -> (Element, Bool)}. We
obviously cannot create a \texttt{Signal (Tree (Signal Element, Signal Bool))}
because that would constitute a signal of signals.  Therefore, we would need to
create a function of type \texttt{Tree String -> Tree (Element, Bool)} and then
\texttt{lift} it onto the \texttt{Signal (Tree String)}. However, since we
cannot write the hovering function of type \texttt{Element -> (Element, Bool)},
this is impossible.  Therefore, we cannot detect hoverable information on the
\texttt{Signal (Tree String)}. Hover information requires a (distinct) signal at
each item in the tree.
